M-M paper, morphological dependence, red sequence

### 2015-04-19 papers/MbhMsph/mm.tex
monmorn

\begin{table*}
\centering
\caption{Linear regression analysis. {\bf X0 is the average X of the subsample...}}
\begin{tabular}{llccccc}
\hline
\hline
{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol X_0$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
\hline 
\\
 & \multicolumn{6}{l}{\emph{Black hole mass -- spheroid luminosity}} \\
 & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm sph} - X_0)/{\rm mag}]$} \\ [0.5em]
All (66)	       & BCES OLS$(Y|X)$   & $8.16 \pm 0.07$ & $-0.44 \pm 0.04$ & $-23.86$ & $-$ & $0.56$ \\
		       & BCES OLS$(X|Y)$   & $8.16 \pm 0.08$ & $-0.61 \pm 0.05$ & $-23.86$ & $-$ & $0.68$ \\
		       & BCES Bisector     & $8.16 \pm 0.07$ & $-0.52 \pm 0.04$ & $-23.86$ & $-$ & $0.60$ \\
		       & mFITEXY OLS$(Y|X)$ & $8.17^{+0.07}_{-0.06}$ & $-0.43^{+0.03}_{-0.03}$ & $-23.86$ & $0.49$ & $0.56$ \\
		       & mFITEXY OLS$(X|Y)$ & $8.15^{+0.07}_{-0.07}$ & $-0.61^{+0.04}_{-0.05}$ & $-23.86$ & $0.96$ & $0.67$ \\
		       & mFITEXY Bisector   & $8.16^{+0.07}_{-0.07}$ & $-0.51^{+0.04}_{-0.04}$ & $-23.86$ & $-$    & $0.60$ \\

$n>2$ (43)	       & BCES OLS$(Y|X)$   & $8.58 \pm 0.07$ & $-0.42 \pm 0.06$ & $-24.77$ & $-$ & $0.46$ \\
		       & BCES OLS$(X|Y)$   & $8.58 \pm 0.08$ & $-0.58 \pm 0.06$ & $-24.77$ & $-$ & $0.56$ \\
		       & BCES Bisector     & $8.58 \pm 0.07$ & $-0.50 \pm 0.05$ & $-24.77$ & $-$ & $0.49$ \\
		       & mFITEXY OLS$(Y|X)$ & $8.57^{+0.07}_{-0.06}$ & $-0.41^{+0.04}_{-0.04}$ & $-24.77$ & $0.38$ & $0.46$ \\
		       & mFITEXY OLS$(X|Y)$ & $8.56^{+0.08}_{-0.08}$ & $-0.57^{+0.06}_{-0.07}$ & $-24.77$ & $0.78$ & $0.55$ \\
		       & mFITEXY Bisector   & $8.57^{+0.07}_{-0.07}$ & $-0.49^{+0.05}_{-0.05}$ & $-24.77$ & $-$    & $0.49$ \\

Core-S\'ersic (22) & BCES OLS$(Y|X)$   & $9.06 \pm 0.09$ & $-0.3  \pm 0.1$  & $-25.73$ & $-$    & $0.42$ \\ 
                   & BCES OLS$(X|Y)$   & $9.1  \pm 0.1$  & $-0.6  \pm 0.1$  & $-25.73$ & $-$    & $0.61$ \\
                   & BCES Bisector     & $9.1  \pm 0.1$  & $-0.47 \pm 0.08$ & $-25.73$ & $-$    & $0.48$ \\
                   & mFITEXY OLS$(Y|X)$ & $9.06^{+0.09}_{-0.08}$ & $-0.26^{+0.07}_{-0.08}$ & $-25.73$ & $0.37$ & $0.42$ \\
                   & mFITEXY OLS$(X|Y)$ & $9.0^{+0.1}_{-0.1}$ & $-0.7^{+0.2}_{-0.3}$ & $-25.73$ & $0.85$ & $0.67$ \\
                   & mFITEXY Bisector   & $9.0^{+0.1}_{-0.1}$ & $-0.5^{+0.1}_{-0.2}$ & $-25.73$ & $-$    & $0.48$ \\

S\'ersic (44) & BCES OLS$(Y|X)$   & $7.71 \pm 0.09$ & $-0.41 \pm 0.08$ & $-22.92$ & $-$    & $0.61$ \\
              & BCES OLS$(X|Y)$   & $7.7  \pm 0.1$  & $-0.9  \pm 0.2 $ & $-22.92$ & $-$    & $0.93$ \\
              & BCES Bisector     & $7.7  \pm 0.1$  & $-0.61 \pm 0.08$ & $-22.92$ & $-$    & $0.71$ \\
              & mFITEXY OLS$(Y|X)$ & $7.72^{+0.08}_{-0.08}$ & ${-0.41}^{+0.07}_{-0.07}$ & $-22.92$ & $0.54$ & $0.61$ \\
              & mFITEXY OLS$(X|Y)$ & $7.7^{+0.1}_{-0.1}$ & $-0.9^{+0.1}_{-0.2}$ & $-22.92$ & $0.89$ & $0.93$ \\
              & mFITEXY Bisector   & $7.7^{+0.1}_{-0.1}$ & $-0.61^{+0.09}_{-0.12}$ & $-22.92$ & $-$	& $0.71$ \\

%Ellipticals (E) (30)   & BCES OLS$(Y|X)$   & $8.80 \pm 0.07$ & $-0.53 \pm 0.09$ & $-25.45$ & $-$    & $0.42$ \\
% 		       & BCES OLS$(X|Y)$   & $8.80 \pm 0.08$ & $-0.66 \pm 0.07$ & $-25.45$ & $-$    & $0.48$ \\
% 		       & BCES Bisector     & $8.80 \pm 0.08$ & $-0.59 \pm 0.07$ & $-25.45$ & $-$    & $0.44$ \\
% 		       & FITEXY OLS$(Y|X)$ & $8.81^{+0.07}_{-0.07}$ & $-0.44^{+0.06}_{-0.07}$ & $-25.45$ & $0.33$     & $0.40$ \\
% 		       & FITEXY OLS$(X|Y)$ & $8.78^{+0.09}_{-0.09}$ & $-0.7^{+0.1}_{-0.1}$    & $-25.45$ & $0.60$     & $0.50$\\
% 		       & FITEXY Bisector   & $8.80^{+0.08}_{-0.08}$ & $-0.56^{+0.08}_{-0.10}$ & $-25.45$ & $-$        & $0.43$ \\
%
%Lenticulars (S0) (13)  & BCES OLS$(Y|X)$   & $7.9 \pm 0.1$ & $-0.4 \pm 0.2$ & $-22.19$ & $-$    & $0.56$ \\
% 		       & BCES OLS$(X|Y)$   & $7.9 \pm 0.3$ & $-1.1 \pm 0.5$ & $-22.19$ & $-$    & $1.01$ \\
% 		       & BCES Bisector     & $7.9 \pm 0.2$ & $-0.7 \pm 0.2$ & $-22.19$ & $-$    & $0.69$ \\
% 		       & FITEXY OLS$(Y|X)$ & $7.9^{+0.2}_{-0.1}$ & $-0.3^{+0.2}_{-0.2}$ & $-22.19$ & $0.51$     & $0.56$ \\
% 		       & FITEXY OLS$(X|Y)$ & $7.8^{+0.3}_{-0.4}$ & $-1.3^{+0.4}_{-1.3}$ & $-22.19$ & $0.71$     & $1.20$\\
% 		       & FITEXY Bisector   & $7.9^{+0.2}_{-0.3}$ & $-0.7^{+0.3}_{-0.4}$ & $-22.19$ & $-$        & $0.71$ \\
%
{\bf Early-type (E+S0)} (45) & BCES OLS$(Y|X)$    & $8.56 \pm 0.07$ & $-0.33 \pm 0.04$ & $-24.47$ & $-$    & $0.46$ \\
 		      	     & BCES OLS$(X|Y)$    & $8.56 \pm 0.08$ & $-0.48 \pm 0.05$ & $-24.47$ & $-$    & $0.55$ \\
 		      	     & {\bf BCES Bisector}& $\boldsymbol{8.56 \pm 0.07}$ & $\boldsymbol{-0.40 \pm 0.04}$ & $\boldsymbol{-24.47}$ & $-$    & $\boldsymbol{0.49}$ \\
 		      	     & mFITEXY OLS$(Y|X)$ & $8.56^{+0.06}_{-0.06}$ & $-0.32^{+0.03}_{-0.04}$ & $-24.47$ & $0.40$ & $0.46$ \\
 		      	     & mFITEXY OLS$(X|Y)$ & $8.54^{+0.08}_{-0.08}$ & $-0.49^{+0.05}_{-0.06}$ & $-24.47$ & $1.00$ & $0.57$\\
 		      	     & mFITEXY Bisector   & $8.55^{+0.07}_{-0.07}$ & $-0.41^{+0.04}_{-0.05}$ & $-24.47$ & $-$	 & $0.49$ \\

{\bf Late-type (Sp)} (17) & BCES OLS$(Y|X)$    & $7.2 \pm 0.2$ & $-0.8 \pm 0.4$ & $-22.33$ & $-$    & $0.70$ \\
 		   	  & BCES OLS$(X|Y)$    & $7.2 \pm 0.3$ & $-1.7 \pm 0.7$ & $-22.33$ & $-$    & $1.26$ \\
 		   	  & {\bf BCES Bisector}& $\boldsymbol{7.2 \pm 0.2}$ & $\boldsymbol{-1.1 \pm 0.3}$ & $\boldsymbol{-22.33}$ & $-$    & $\boldsymbol{0.88}$ \\
 		   	  & mFITEXY OLS$(Y|X)$ & $7.2^{+0.1}_{-0.1}$ & $-0.5^{+0.2}_{-0.2}$ & $-22.33$ & $0.54$ & $0.63$ \\
 		   	  & mFITEXY OLS$(X|Y)$ & $7.4^{+0.5}_{-0.3}$ & $-2.0^{+0.7}_{-2.3}$ & $-22.33$ & $0.54$ & $1.51$ \\
 		   	  & mFITEXY Bisector   & $7.3^{+0.4}_{-0.3}$ & $-1.0^{+0.3}_{-0.5}$ & $-22.33$ & $-$	& $0.82$ \\
\hline 
\\
 & \multicolumn{6}{l}{\emph{Black hole mass -- galaxy luminosity}} \\
  & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm gal} - X_0)/{\rm mag}]$} \\ [0.5em]
All (62)               & BCES OLS$(Y|X)$   & $8.26 \pm 0.08$ & $-0.49 \pm 0.06$ & $-24.78$ & $-$ & $0.64$ \\
 		       & BCES OLS$(X|Y)$   & $8.3 \pm 0.1$   & $-1.0 \pm 0.1$   & $-24.78$ & $-$ & $0.92$ \\
 		       & BCES Bisector     & $8.26 \pm 0.09$ & $-0.72 \pm 0.07$ & $-24.78$ & $-$ & $0.71$ \\
 		       & mFITEXY OLS$(Y|X)$ & $8.26^{+0.08}_{-0.08}$ & $-0.48^{+0.06}_{-0.07}$ & $-24.78$ & $0.62$ & $0.64$ \\
 		       & mFITEXY OLS$(X|Y)$ & $8.3^{+0.1}_{-0.1}$    & $-1.0^{+0.1}_{-0.2}$    & $-24.78$ & $0.87$ & $0.93$ \\
 		       & mFITEXY Bisector   & $8.3^{+0.1}_{-0.1}$    & $-0.72^{+0.08}_{-0.10}$ & $-24.78$ & $-$    & $0.71$ \\

Early-type (E+S0) (45) & BCES OLS$(Y|X)$   & $8.56 \pm 0.06$ & $-0.43 \pm 0.05$ & $-24.88$ & $-$ & $0.45$ \\
 		       & BCES OLS$(X|Y)$   & $8.56 \pm 0.08$ & $-0.63 \pm 0.05$ & $-24.88$ & $-$ & $0.53$ \\
 		       & BCES Bisector     & $8.56 \pm 0.07$ & $-0.53 \pm 0.04$ & $-24.88$ & $-$ & $0.47$ \\
 		       & mFITEXY OLS$(Y|X)$ & $8.56^{+0.06}_{-0.06}$ & $-0.41^{+0.05}_{-0.05}$ & $-24.88$ & $0.41$ & $0.45$ \\
 		       & mFITEXY OLS$(X|Y)$ & $8.56^{+0.07}_{-0.09}$ & $-0.66^{+0.06}_{-0.08}$ & $-24.88$ & $0.79$ & $0.55$ \\
 		       & mFITEXY Bisector   & $8.56^{+0.07}_{-0.07}$ & $-0.53^{+0.05}_{-0.07}$ & $-24.88$ & $-$    & $0.47$ \\

%All (62)		& BCES OLS$(Y|X)$   & $$ & $$ & $$ & $-$ & $$ \\
%			& BCES OLS$(X|Y)$   & $$ & $$ & $$ & $-$ & $$ \\
%			& BCES Bisector     & $$ & $$ & $$ & $-$ & $$ \\
%			& FITEXY OLS$(Y|X)$ & $$ & $$ & $$ & $$ & $$ \\
%			& FITEXY OLS$(X|Y)$ & $$ & $$ & $$ & $$ & $$ \\
%			& FITEXY Bisector   & $$ & $$ & $$ & $-$    & $$ \\
\hline 
\\
 & \multicolumn{6}{l}{\emph{Black hole mass -- spheroid stellar mass}} \\
  & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta \log[(M_{\rm *,sph} - X_0)/{\rm M_\odot}]$} \\ [0.5em]
{\bf Early-type (E+S0)} (45)  & BCES OLS$(Y|X)$    & $8.56 \pm 0.07$ & $0.8 \pm 0.1$ & $10.81$ & $-$ & $0.48$ \\
		      	      & BCES OLS$(X|Y)$    & $8.56 \pm 0.08$ & $1.3 \pm 0.1$ & $10.81$ & $-$ & $0.59$ \\
		      	      & {\bf BCES Bisector}& $\boldsymbol{8.56 \pm 0.07}$ & $\boldsymbol{1.0 \pm 0.1}$ & $\boldsymbol{10.81}$ & $-$ & $\boldsymbol{0.51}$ \\
		      	      & FITEXY OLS$(Y|X)$  & $$ & $$ & $10.81$ & $$ & $$ \\
		      	      & FITEXY OLS$(X|Y)$  & $$ & $$ & $10.81$ & $$ & $$ \\
		      	      & FITEXY Bisector    & $$ & $$ & $10.81$ & $-$    & $$ \\

{\bf Late-type (Sp)} (17)    & BCES OLS$(Y|X)$    & $7.2 \pm 0.2$ & $1.9 \pm 1.5$ & $10.05$ & $-$ & $0.74$ \\
		     	     & BCES OLS$(X|Y)$    & $7.2 \pm 0.4$ & $5.9 \pm 3.4$ & $10.05$ & $-$ & $1.70$ \\
		     	     & {\bf BCES Bisector}& $\boldsymbol{7.2 \pm 0.2}$ & $\boldsymbol{3.0 \pm 1.3}$ & $\boldsymbol{10.05}$ & $-$ & $\boldsymbol{0.94}$ \\
		     	     & FITEXY OLS$(Y|X)$  & $$ & $$ & $10.05$ & $$ & $$ \\
		     	     & FITEXY OLS$(X|Y)$  & $$ & $$ & $10.05$ & $$ & $$ \\
		     	     & FITEXY Bisector    & $$ & $$ & $10.05$ & $-$    & $$ \\

>>>>

\begin{table*}
\centering
\caption{Linear regression analysis. {\bf X0 is the average X of the subsample...}}
\begin{tabular}{llccccc}
\hline
\hline
{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol X_0$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
\hline 
\\
 & \multicolumn{6}{l}{\emph{Black hole mass -- spheroid luminosity}} \\
 & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm sph} - X_0)/{\rm mag}]$} \\ [0.5em]
All (66)               & BCES OLS$(Y|X)$   & $8.16 \pm 0.07$ & $-0.44 \pm 0.04$ & $-23.86$ & $-$ & $0.56$ \\
                       & BCES OLS$(X|Y)$   & $8.16 \pm 0.08$ & $-0.61 \pm 0.05$ & $-23.86$ & $-$ & $0.68$ \\
                       & BCES Bisector     & $8.16 \pm 0.07$ & $-0.52 \pm 0.04$ & $-23.86$ & $-$ & $0.60$ \\
                       & mFITEXY OLS$(Y|X)$ & $8.17^{+0.07}_{-0.06}$ & $-0.43^{+0.03}_{-0.03}$ & $-23.86$ & $0.49$ & $0.56$ \\
                       & mFITEXY OLS$(X|Y)$ & $8.15^{+0.07}_{-0.07}$ & $-0.61^{+0.04}_{-0.05}$ & $-23.86$ & $0.96$ & $0.67$ \\
                       & mFITEXY Bisector   & $8.16^{+0.07}_{-0.07}$ & $-0.51^{+0.04}_{-0.04}$ & $-23.86$ & $-$    & $0.60$ \\
                       & Kelly OLS$(Y|X)$  & $8.16 \pm 0.07$ & $-0.42 \pm 0.04$ & $-23.86$ & $0.51 \pm 0.06$ & $0.56$ \\
                       & Kelly OLS$(X|Y)$  & $8.16 \pm 0.09$ & $-0.60 \pm 0.06$ & $-23.86$ & $0.6 \pm 0.1$ & $0.67$ \\
                       & Kelly Bisector    & $$ & $$ & $-23.86$ & $-$    & $$ \\

$n>2$ (43)             & BCES OLS$(Y|X)$   & $8.58 \pm 0.07$ & $-0.42 \pm 0.06$ & $-24.77$ & $-$ & $0.46$ \\
                       & BCES OLS$(X|Y)$   & $8.58 \pm 0.08$ & $-0.58 \pm 0.06$ & $-24.77$ & $-$ & $0.56$ \\
                       & BCES Bisector     & $8.58 \pm 0.07$ & $-0.50 \pm 0.05$ & $-24.77$ & $-$ & $0.49$ \\
                       & mFITEXY OLS$(Y|X)$ & $8.57^{+0.07}_{-0.06}$ & $-0.41^{+0.04}_{-0.04}$ & $-24.77$ & $0.38$ & $0.46$ \\
                       & mFITEXY OLS$(X|Y)$ & $8.56^{+0.08}_{-0.08}$ & $-0.57^{+0.06}_{-0.07}$ & $-24.77$ & $0.78$ & $0.55$ \\
                       & mFITEXY Bisector   & $8.57^{+0.07}_{-0.07}$ & $-0.49^{+0.05}_{-0.05}$ & $-24.77$ & $-$    & $0.49$ \\
                       & Kelly OLS$(Y|X)$  & $8.56 \pm 0.07$ & $-0.39 \pm 0.05$ & $-24.77$ & $0.41 \pm 0.06$ & $0.46$ \\
                       & Kelly OLS$(X|Y)$  & $8.55 \pm 0.09$ & $-0.59 \pm 0.08$ & $-24.77$ & $0.5 \pm  0.1$ & $0.56$ \\
                       & Kelly Bisector    & $$ & $$ & $-24.77$ & $-$    & $$ \\

Core-S\'ersic (22) & BCES OLS$(Y|X)$   & $9.06 \pm 0.09$ & $-0.3  \pm 0.1$  & $-25.73$ & $-$    & $0.42$ \\ 
                   & BCES OLS$(X|Y)$   & $9.1  \pm 0.1$  & $-0.6  \pm 0.1$  & $-25.73$ & $-$    & $0.61$ \\
                   & BCES Bisector     & $9.1  \pm 0.1$  & $-0.47 \pm 0.08$ & $-25.73$ & $-$    & $0.48$ \\
                   & mFITEXY OLS$(Y|X)$ & $9.06^{+0.09}_{-0.08}$ & $-0.26^{+0.07}_{-0.08}$ & $-25.73$ & $0.37$ & $0.42$ \\
                   & mFITEXY OLS$(X|Y)$ & $9.0^{+0.1}_{-0.1}$ & $-0.7^{+0.2}_{-0.3}$ & $-25.73$ & $0.85$ & $0.67$ \\
                   & mFITEXY Bisector   & $9.0^{+0.1}_{-0.1}$ & $-0.5^{+0.1}_{-0.2}$ & $-25.73$ & $-$    & $0.48$ \\
                   & Kelly OLS$(Y|X)$  & $9.0 \pm 0.1$ & $-0.24 \pm 0.09$ & $-25.73$ & $0.41 \pm 0.09$ & $0.42$ \\
                   & Kelly OLS$(X|Y)$  & $$ & $$ & $-25.73$ & $$ & $$ \\
                   & Kelly Bisector    & $$ & $$ & $-25.73$ & $-$    & $$ \\

S\'ersic (44) & BCES OLS$(Y|X)$   & $7.71 \pm 0.09$ & $-0.41 \pm 0.08$ & $-22.92$ & $-$    & $0.61$ \\
              & BCES OLS$(X|Y)$   & $7.7  \pm 0.1$  & $-0.9  \pm 0.2 $ & $-22.92$ & $-$    & $0.93$ \\
              & BCES Bisector     & $7.7  \pm 0.1$  & $-0.61 \pm 0.08$ & $-22.92$ & $-$    & $0.71$ \\
              & mFITEXY OLS$(Y|X)$ & $7.72^{+0.08}_{-0.08}$ & ${-0.41}^{+0.07}_{-0.07}$ & $-22.92$ & $0.54$ & $0.61$ \\
              & mFITEXY OLS$(X|Y)$ & $7.7^{+0.1}_{-0.1}$ & $-0.9^{+0.1}_{-0.2}$ & $-22.92$ & $0.89$ & $0.93$ \\
              & mFITEXY Bisector   & $7.7^{+0.1}_{-0.1}$ & $-0.61^{+0.09}_{-0.12}$ & $-22.92$ & $-$     & $0.71$ \\
              & Kelly OLS$(Y|X)$  & $7.72 \pm 0.09$ & $-0.41 \pm 0.09$ & $-22.92$ & $0.55 \pm 0.08$ & $0.61$ \\
              & Kelly OLS$(X|Y)$  & $7.7 \pm  0.1$ & $-0.9 \pm  0.2$ & $-22.92$ & $0.8 \pm  0.3$ & $0.98$ \\
              & Kelly Bisector    & $$ & $$ & $-22.92$ & $-$    & $$ \\

%Ellipticals (E) (30)   & BCES OLS$(Y|X)$   & $8.80 \pm 0.07$ & $-0.53 \pm 0.09$ & $-25.45$ & $-$    & $0.42$ \\
%                      & BCES OLS$(X|Y)$   & $8.80 \pm 0.08$ & $-0.66 \pm 0.07$ & $-25.45$ & $-$    & $0.48$ \\
%                      & BCES Bisector     & $8.80 \pm 0.08$ & $-0.59 \pm 0.07$ & $-25.45$ & $-$    & $0.44$ \\
%                      & FITEXY OLS$(Y|X)$ & $8.81^{+0.07}_{-0.07}$ & $-0.44^{+0.06}_{-0.07}$ & $-25.45$ & $0.33$     & $0.40$ \\
%                      & FITEXY OLS$(X|Y)$ & $8.78^{+0.09}_{-0.09}$ & $-0.7^{+0.1}_{-0.1}$    & $-25.45$ & $0.60$     & $0.50$\\
%                      & FITEXY Bisector   & $8.80^{+0.08}_{-0.08}$ & $-0.56^{+0.08}_{-0.10}$ & $-25.45$ & $-$        & $0.43$ \\
%
%Lenticulars (S0) (13)  & BCES OLS$(Y|X)$   & $7.9 \pm 0.1$ & $-0.4 \pm 0.2$ & $-22.19$ & $-$    & $0.56$ \\
%                      & BCES OLS$(X|Y)$   & $7.9 \pm 0.3$ & $-1.1 \pm 0.5$ & $-22.19$ & $-$    & $1.01$ \\
%                      & BCES Bisector     & $7.9 \pm 0.2$ & $-0.7 \pm 0.2$ & $-22.19$ & $-$    & $0.69$ \\
%                      & FITEXY OLS$(Y|X)$ & $7.9^{+0.2}_{-0.1}$ & $-0.3^{+0.2}_{-0.2}$ & $-22.19$ & $0.51$     & $0.56$ \\
%                      & FITEXY OLS$(X|Y)$ & $7.8^{+0.3}_{-0.4}$ & $-1.3^{+0.4}_{-1.3}$ & $-22.19$ & $0.71$     & $1.20$\\
%                      & FITEXY Bisector   & $7.9^{+0.2}_{-0.3}$ & $-0.7^{+0.3}_{-0.4}$ & $-22.19$ & $-$        & $0.71$ \\
%
{\bf Early-type (E+S0)} (45) & BCES OLS$(Y|X)$    & $8.56 \pm 0.07$ & $-0.33 \pm 0.04$ & $-24.47$ & $-$    & $0.46$ \\
                             & BCES OLS$(X|Y)$    & $8.56 \pm 0.08$ & $-0.48 \pm 0.05$ & $-24.47$ & $-$    & $0.55$ \\
                             & {\bf BCES Bisector}& $\boldsymbol{8.56 \pm 0.07}$ & $\boldsymbol{-0.40 \pm 0.04}$ & $\boldsymbol{-24.47}$ & $-$    & $\boldsymbol{0.49}$ \\
                             & mFITEXY OLS$(Y|X)$ & $8.56^{+0.06}_{-0.06}$ & $-0.32^{+0.03}_{-0.04}$ & $-24.47$ & $0.40$ & $0.46$ \\
                             & mFITEXY OLS$(X|Y)$ & $8.54^{+0.08}_{-0.08}$ & $-0.49^{+0.05}_{-0.06}$ & $-24.47$ & $1.00$ & $0.57$\\
                             & mFITEXY Bisector   & $8.55^{+0.07}_{-0.07}$ & $-0.41^{+0.04}_{-0.05}$ & $-24.47$ & $-$    & $0.49$ \\
                             & Kelly OLS$(Y|X)$  & $8.55 \pm 0.07$ & $-0.32 \pm 0.04$ & $-24.47$ & $0.42 \pm 0.06$ & $ 0.46$ \\
                             & Kelly OLS$(X|Y)$  & $8.55 \pm 0.09$ & $-0.49 \pm 0.07$ & $-24.47$ & $0.5 \pm  0.1$ & $0.57$ \\
                             & Kelly Bisector    & $$ & $$ & $-24.47$ & $-$    & $$ \\

{\bf Late-type (Sp)} (17) & BCES OLS$(Y|X)$    & $7.2 \pm 0.2$ & $-0.8 \pm 0.4$ & $-22.33$ & $-$    & $0.70$ \\
                          & BCES OLS$(X|Y)$    & $7.2 \pm 0.3$ & $-1.7 \pm 0.7$ & $-22.33$ & $-$    & $1.26$ \\
                          & {\bf BCES Bisector}& $\boldsymbol{7.2 \pm 0.2}$ & $\boldsymbol{-1.1 \pm 0.3}$ & $\boldsymbol{-22.33}$ & $-$    & $\boldsymbol{0.88}$ \\
                          & mFITEXY OLS$(Y|X)$ & $7.2^{+0.1}_{-0.1}$ & $-0.5^{+0.2}_{-0.2}$ & $-22.33$ & $0.54$ & $0.63$ \\
                          & mFITEXY OLS$(X|Y)$ & $7.4^{+0.5}_{-0.3}$ & $-2.0^{+0.7}_{-2.3}$ & $-22.33$ & $0.54$ & $1.51$ \\
                          & mFITEXY Bisector   & $7.3^{+0.4}_{-0.3}$ & $-1.0^{+0.3}_{-0.5}$ & $-22.33$ & $-$    & $0.82$ \\
                          & Kelly OLS$(Y|X)$  & $7.2 \pm 0.2$ & $-0.5 \pm 0.3$ & $-22.33$ & $0.6 \pm 0.2$ & $0.62$ \\
                          & Kelly OLS$(X|Y)$  & $$ & $$ & $-22.33$ & $$ & $$ \\
                          & Kelly Bisector    & $$ & $$ & $-22.33$ & $-$    & $$ \\

\hline 
\\
 & \multicolumn{6}{l}{\emph{Black hole mass -- galaxy luminosity}} \\
  & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm gal} - X_0)/{\rm mag}]$} \\ [0.5em]
All (62)               & BCES OLS$(Y|X)$   & $8.26 \pm 0.08$ & $-0.49 \pm 0.06$ & $-24.78$ & $-$ & $0.64$ \\
                       & BCES OLS$(X|Y)$   & $8.3 \pm 0.1$   & $-1.0 \pm 0.1$   & $-24.78$ & $-$ & $0.92$ \\
                       & BCES Bisector     & $8.26 \pm 0.09$ & $-0.72 \pm 0.07$ & $-24.78$ & $-$ & $0.71$ \\
                       & mFITEXY OLS$(Y|X)$ & $8.26^{+0.08}_{-0.08}$ & $-0.48^{+0.06}_{-0.07}$ & $-24.78$ & $0.62$ & $0.64$ \\
                       & mFITEXY OLS$(X|Y)$ & $8.3^{+0.1}_{-0.1}$    & $-1.0^{+0.1}_{-0.2}$    & $-24.78$ & $0.87$ & $0.93$ \\
                       & mFITEXY Bisector   & $8.3^{+0.1}_{-0.1}$    & $-0.72^{+0.08}_{-0.10}$ & $-24.78$ & $-$    & $0.71$ \\
                       & Kelly OLS$(Y|X)$  & $8.26 \pm 0.08$ & $-0.48 \pm 0.07$ & $-24.78$ & $0.63 \pm 0.06$ & $0.64$ \\
                       & Kelly OLS$(X|Y)$  & $8.3 \pm 0.1$ & $-1.0 \pm 0.2$ & $-24.78$ & $0.9 \pm 0.2$ & $0.96$ \\
                       & Kelly Bisector    & $$ & $$ & $-24.78$ & $-$    & $$ \\

Early-type (E+S0) (45) & BCES OLS$(Y|X)$   & $8.56 \pm 0.06$ & $-0.43 \pm 0.05$ & $-24.88$ & $-$ & $0.45$ \\
                       & BCES OLS$(X|Y)$   & $8.56 \pm 0.08$ & $-0.63 \pm 0.05$ & $-24.88$ & $-$ & $0.53$ \\
                       & BCES Bisector     & $8.56 \pm 0.07$ & $-0.53 \pm 0.04$ & $-24.88$ & $-$ & $0.47$ \\
                       & mFITEXY OLS$(Y|X)$ & $8.56^{+0.06}_{-0.06}$ & $-0.41^{+0.05}_{-0.05}$ & $-24.88$ & $0.41$ & $0.45$ \\
                       & mFITEXY OLS$(X|Y)$ & $8.56^{+0.07}_{-0.09}$ & $-0.66^{+0.06}_{-0.08}$ & $-24.88$ & $0.79$ & $0.55$ \\
                       & mFITEXY Bisector   & $8.56^{+0.07}_{-0.07}$ & $-0.53^{+0.05}_{-0.07}$ & $-24.88$ & $-$    & $0.47$ \\
                       & Kelly OLS$(Y|X)$  & $8.56 \pm 0.07$ & $-0.42 \pm 0.06$ & $-24.88$ & $0.44 \pm 0.06$ & $0.45$ \\
                       & Kelly OLS$(X|Y)$  & $8.56 \pm 0.09$ & $-0.66 \pm 0.09$ & $-24.88$ & $0.6 \pm 0.1$ & $0.55$ \\
                       & Kelly Bisector    & $$ & $$ & $-24.88$ & $-$    & $$ \\

%All (62)               & BCES OLS$(Y|X)$   & $$ & $$ & $$ & $-$ & $$ \\
%                       & BCES OLS$(X|Y)$   & $$ & $$ & $$ & $-$ & $$ \\
%                       & BCES Bisector     & $$ & $$ & $$ & $-$ & $$ \\
%                       & FITEXY OLS$(Y|X)$ & $$ & $$ & $$ & $$ & $$ \\
%                       & FITEXY OLS$(X|Y)$ & $$ & $$ & $$ & $$ & $$ \\
%                       & FITEXY Bisector   & $$ & $$ & $$ & $-$    & $$ \\
%                       & Kelly OLS$(Y|X)$  & $$ & $$ & $$ & $$ & $$ \\
%                       & Kelly OLS$(X|Y)$  & $$ & $$ & $$ & $$ & $$ \\
%                       & Kelly Bisector    & $$ & $$ & $$ & $-$    & $$ \\

\hline 
\\
 & \multicolumn{6}{l}{\emph{Black hole mass -- spheroid stellar mass}} \\
  & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta \log[(M_{\rm *,sph} - X_0)/{\rm M_\odot}]$} \\ [0.5em]
{\bf Early-type (E+S0)} (45)  & BCES OLS$(Y|X)$    & $8.56 \pm 0.07$ & $0.8 \pm 0.1$ & $10.81$ & $-$ & $0.48$ \\
                              & BCES OLS$(X|Y)$    & $8.56 \pm 0.08$ & $1.3 \pm 0.1$ & $10.81$ & $-$ & $0.59$ \\
                              & {\bf BCES Bisector}& $\boldsymbol{8.56 \pm 0.07}$ & $\boldsymbol{1.0 \pm 0.1}$ & $\boldsymbol{10.81}$ & $-$ & $\boldsymbol{0.51}$ \\
                              & FITEXY OLS$(Y|X)$  & $$ & $$ & $10.81$ & $$ & $$ \\
                              & FITEXY OLS$(X|Y)$  & $$ & $$ & $10.81$ & $$ & $$ \\
                              & FITEXY Bisector    & $$ & $$ & $10.81$ & $-$    & $$ \\
                              & Kelly OLS$(Y|X)$  & $8.55 \pm 0.07$ & $0.8 \pm 0.1$ & $10.81$ & $0.43 \pm 0.06$ & $0.48$ \\
                              & Kelly OLS$(X|Y)$  & $8.55 \pm 0.09$ & $1.3 \pm  0.2$ & $10.81$ & $0.6 \pm  0.1$ & $0.61$ \\
                              & Kelly Bisector    & $$ & $$ & $10.81$ & $-$    & $$ \\
